\Title

### 2023-06-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

After training our model, we first analyze the weights learned for the different neurons (\seeFig{kernels}). We first notice by following each spatial pattern from the shortest delay (right) to the longest that the selectivity of these cells are very localized and are transported around linear trajectories in the space-delay space. These show also a relative selectivity to the orientation perpendicular to motion, similarly to what is found for MT neurons~\citep{deangelis_functional_1999}. This reflects the way events are generated and in particular the so-called aperture problem which implies that an line moving along its axis would generate no change in luminance and therefore generate no event. Focusing on the positive weights, a strong selectivity along specific motion axes is observed for each of the different kernels. These directions can be easily associated with the direction of motion controlled in the natural images and show a typical anisotropic profile~\citep{kaplan_anisotropic_2013}. The negative weights surround these positive weights, providing an enhanced response. For example, the first kernel shows a strong selectivity for a downward direction of motion. Note that as the delays become larger, two effects can be remarked. First, coefficients become lower which is consistent with the fact that trajectories are defined in a piecewise fashion, such that such decrease provides with an optimal integration with respect to this limited memory. Second, coefficients become less localized compared to the kerenl's spatial profile at short delays, consistent with the average diffusion of information included in the generative model and with the diffusion introduced in motion-based prediction models~\citep{perrinet_motion-based_2012,khoei_flash-lag_2017}. We also observed a strong dependence between the weights reaching the ON polarities and those reaching the OFF polarities. In particular, whenever a weight for a given position and delay is positive for one polarity, it will be negative for the other. This property is due to the way the events are generated and the fact that the luminance cannot increase and decrease at the same time.  Interestingly, the relative organization of the receptive fields in quadrature of phase follows a push-pull organization predicted by~\citet{kremkow_push-pull_2016} to explain neurophysiological results obtained after showing similar natural scenes with synthetic eye movements~\citep{baudot_animation_2013}.

>>>>

After training our model, let us first analyze the weights learned for the different neurons (\seeFig{kernels}). We first notice by following each spatial pattern from the shortest delay (right) to the longest that the selectivity of these cells are very localized and are transported along linear trajectories in the space-delay space. These show also a relative selectivity to the orientation perpendicular to motion, similarly to what is found for MT neurons~\citep{deangelis_functional_1999}. This reflects the way events are generated and in particular the so-called aperture problem which implies that an line moving along its axis would generate no change in luminance and therefore generate no event. Focusing on the positive weights, a strong selectivity along specific motion axes is observed for each of the different kernels. These directions can be easily associated with the direction of motion controlled in the natural images and show a typical anisotropic profile~\citep{kaplan_anisotropic_2013}. The negative weights surround these positive weights, providing an enhanced response. For example, the first kernel shows a strong selectivity for a downward direction of motion. Note that as the delays become larger, two effects can be remarked. First, coefficients become lower which is consistent with the fact that trajectories are defined in a piecewise fashion, such that such decrease provides with an optimal integration with respect to this limited memory. Second, coefficients become less localized compared to the kerenl's spatial profile at short delays, consistent with the average diffusion of information included in the generative model and with the diffusion introduced in motion-based prediction models~\citep{perrinet_motion-based_2012,khoei_flash-lag_2017}. We also observed a strong dependence between the weights reaching the ON polarities and those reaching the OFF polarities. In particular, whenever a weight for a given position and delay is positive for one polarity, it will be negative for the other. This property is due to the way the events are generated and the fact that the luminance cannot increase and decrease at the same time.  Interestingly, the relative organization of the receptive fields in quadrature of phase follows a push-pull organization predicted by~\citet{kremkow_push-pull_2016} to explain neurophysiological results obtained after showing similar natural scenes with synthetic eye movements~\citep{baudot_animation_2013}.
